\documentclass{article}
\usepackage{amsmath, amsfonts}
\usepackage{csquotes}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% sets
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}

% funtors and operators
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\End}{\mathrm{End}}

% other
\renewcommand{\th}{^{\mathrm{th}}}

\begin{document}
	\title{Referee reply for ``Chain level Steenrod operations"}
	\date{\today}
	\maketitle
	
	We begin by thanking the referee for their careful reading and many valuable suggestions.
	Below we include a point-by-point reply to the report.
	
	\section{Points raised by the referee}

	\begin{enumerate}
		\item Thank you for pointing this typo.
		We have fixed it and many other similar mistakes.
		\item We have followed all the suggestions presented in this point.
		Explicitly,
		\begin{enumerate}
			\item Change the title from ``Chain level Steenrod operations" to ``Cochain level May-Steenrod operations".
			\item Rename ``Steenrod-Adem structures" to ``May-Steenrod structures''.
			\item Add a paragraph below Definition 7 explaining in more detail the relationship between our notion of May-Steenrod structure and those considered by May in his ``A general algebraic approach to Steenrod operations''.
		\end{enumerate}
		\item
		\begin{enumerate}
			\item We greatly expanded the discussion of Adem and Cartan relations, making explicit their dependence on the proofs by May.
			We have also separated their treatment.
			The Adem relations are a consequence of the fact that a May-Steenrod structure demands a factorization with the second factor a morphism of operads.
			The (internal) Cartan relations require some compatibility with the coalgebra structure on the minimal resolution $\mathcal W$.
			Something that was missing in the previous version of this paper and that we have now corrected by introducing the notion of a ``comultiplicative May-Steenrod structure''.
			\item Add Remark 17 explaining that our map $\mathcal W \to \mathcal E$ factors through the (unreduced) bar resolution of $\mathrm C$, with the second map in the factorization induced from the chosen inclusions $\iota \colon \mathrm C_r \to \mathrm S_r$.
		\end{enumerate}
	\end{enumerate}

	\section{Other changes}
	\begin{enumerate}
		\item We have removed the appendix containing two proofs and a sketch of a third one.
		Specifically, we have moved the proof of Theorem 15 and 24 from the appendix to right below their statement, and replaced the sketch of proof of Proposition 28 with a reference to a complete proof.
		\item To motivate the consideration of the cubical viewpoint, we have included a paragraph in the introduction mentioning Baues' cubical reformulation of Adams' cobar construction.
		This implies that the constructions of this paper provides explicit descriptions of Steenrod operations on the cobar construction of chains of (reduced) simplicial sets
	\end{enumerate}
\end{document}