
\section{May-Steenrod structures}

We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime. It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime. For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.

\begin{definition} \label{def: May-Steenrod structure}
	A \textit{May-Steenrod structure} on an operad $\mathcal O$ is a 
	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
	\begin{equation*}
	\begin{tikzcd}[column sep = normal, row sep = small]
	& \mathcal R \arrow[dr, "\phi", out=0] & \\
	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
	\end{tikzcd}
	\end{equation*}
	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
\end{definition}

\begin{remark} \label{rmk: Deligne conjecture}
	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$. In this language, a choice of factorization for a May-Steenrod structure on $\mathcal O$ defines in particular a \textit{commutative multiplication} on~$\mathcal O$.
\end{remark}

\begin{definition} \label{def: Steenrod products}
	Let $A$ be a chain complex.
	A May-Steenrod structure on $\mathrm{End}_A$ is referred to as one on $A$.
	Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
\end{definition}

Let $A$ be equipped with a May-Steenrod structure
%$\mathcal W \to \mathcal R \to \End_A$.
\begin{equation*}
\begin{tikzcd}[column sep = normal, row sep = small]
& \mathcal R \arrow[dr, "\phi", out=0] & \\
\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \End_A.
\end{tikzcd}
\end{equation*}
We can relate this structure to the language of \cite{may70generalapproach} as follows.
The morphism $\phi$ provides $A$ with the structure of a homotopy associative (and commutative) dg algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
Restricting $\psi$ to arity $r$ defines a map $\theta \colon W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op. cit.
Explicitly, this is the claim that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the interated product $A^{\otimes r} \to A$.
A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathrm R(r)$ and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ an object in May's category $\mathfrak{C}(p, \infty)$.
For elements in this category Definition 2.2 op. cit., reviewed below, defines operations on the mod-$p$ homology of $A$.
In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki-Kudo and Dyer-Lashof.

For the rest of this section $A$ is a chain complex equipped with a May-Steenrod structure.

\begin{definition}
	For any prime $p$, the $\mathbb{F}_p$-linear map
	\begin{equation*}
	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
	\end{equation*}
	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
\end{definition}

We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.

\begin{definition}
	For any integer $s$, the \textit{May-Steenrod operation}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
	\end{equation*}
	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
\end{definition}

Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients. These binary operations are known as cup-$i$ products. In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$. We can explain the appearance of these specific Steenrod products as follows. The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd. According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.

\begin{definition} \label{def: Steenrod operations at odd prime}
	For any integer $s$, the \textit{May-Steenrod operations}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
	\end{equation*}
	and
	\begin{equation*}
	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
	\end{equation*}
	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
	\begin{equation*}
	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
	\end{equation*}
	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
\end{definition}

\begin{remark}
	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod53cyclic}). The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
\end{remark}


BEING A CARTAN OBJECT IS LIKE MORE COMPLICATED AND NOT IMMEDIATE IT SEEMS

Steenrod operations satisfy the Cartan and Adem relations.
Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
\begin{lemma}
	Let $A$ be equipped with a May-Steenrod structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
	\begin{equation*}
	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
	\end{equation*}
	and
	\begin{itemize}
		\item If $p = 2$ and $a > 2b$
		\begin{equation*}
		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
		\end{equation*}
		\item If $p > 2$ and $a > pb$
		\begin{equation*}
		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
		\end{equation*}
	\end{itemize}		
\end{lemma}

\begin{proof}
	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(p, \infty)$.
	Furthermore, this pair is in May's language both a Cartan and an Adem object, meaning that 
	
	and the claim of this lemma is proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
\end{proof}

For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}. For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.

For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.

